---
title: "fatsecretR"
author: "Tom Wilson"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{rmarkdown::render()}
---
## Introduction

`fatsecret` is an freely available application which allows users to keep track of their daily dietary intake. The benefit of `fatsecret` is that is contains a vast dietary database, which enables for users to quickly enter qualitative data on their consumed meals. The `fatsecret` database then translate this meal information into detailed maco and micro nutrient profiles.

This package users the `fatsecret` REST API to allow for a direct interface with `fatsecret` through `R`.  The main objective of `fatsecretR` is to create a tool which will enable for `fatsecret` to be used an electronic diet recording tool in nutritional epidemiology studies. By using the REST API _via_ `R`, data from large study cohorts can be easily accessed, and quickly analysed. The 3-Legged OAuth1.0 Authentication is used to access profiles which study particpants have created. Once paritcipants have granted access to `fatsecretR` their data can be conintuousnly downloaded and analysed throughout the course of study/intervention, with not futher onus on the partipant. The end results is less work for both the partipant and investigator. Finally, as `R` is typically the language of choice for statistical analysis and data visualisation, download raw data directly into `R` is clearly advantageous. 

### Setup

All of the methods contained in the `fatsecret` REST API can be split into two catogries.  Data that is shared between all users and data that is assigned to a single user. For example, the comprehensive food database can be accessed by any API user. However, making an API request on behalf of a user requires slightly more authentication. 

For more information on the `fatsecret` Authentication Protocols, see [here](https://platform.fatsecret.com/api/Default.aspx?screen=rapiauth)





At the start of each `fatsecretR` session your individual Consumer (API) key and Shared Secret key to be passed to the sessions options. These two keys are required for all of the avaialble API methods. The keys shown in these vignette ARE NOT genuine keys, they are just random alphanumeric strings to act as place holders. 


```{r, eval=FALSE}
library(fatsecretR)

options("CONSUMER_KEY" = "e65fc92c9b6a45dbb06e514395aba75b")
options("SHARED_SECRET" = "380822d0460d4a7c8fb53ac9a5ee3e25")
```



```{r, eval - FALSE}
#getFood("beer")
```
