---
title: "fatsecretR"
author: "Tom Wilson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Setup

At the start of each `fatsecretR` session your individual Consumer (API) key and Shared Secret key to be passed to the sessions options. These two keys are required for all of the avaialble API methods. The keys shown in these vignette ARE NOT genuine keys, they are just random alphanumeric strings to act as place holders. 


```{r}
library(fatsecretR)

options("CONSUMER_KEY" = "e65fc92c9b6a45dbb06e514395aba75b")
options("SHARED_SECRET" = "380822d0460d4a7c8fb53ac9a5ee3e25")
```



### Shared Data

The fatsecret API is segmented into two sections. Data that is shared between all users and data that is assigned to a single user. For example, the comprehensive food database can be accessed by any API user. However, making an API request on behalf of a user requires slightly more authentication. 

The available methods are currently focused on retrieving nutritional composition data on a specific food item witihn the data base. 

```{r}
getFood("beer")
```
